---
title: "address sampling"
format: html
editor: visual
---

Designing a survey that ensuring comprehensive representation across census dissemination areas (DAs) and based on best practices in survey sampling:

------------------------------------------------------------------------

### **Objective**

To design a sampling mechanism that ensures: 1. Equal representation across all DAs in the province. 2. Improved accuracy and reliability of survey results at the DA level.

------------------------------------------------------------------------

### **Sampling Plan**

#### **1. Stratification**

Stratification ensures that specific subgroups (strata) are represented in the sample. The stratification criteria could include: 

   -  **Geographic regions**: Divide the province into regions (e.g., urban, suburban, rural).
   -  **Population density**: Group DAs into high, medium, and low-density strata. 
   -  **Socioeconomic indicators**: Consider stratifying by income levels, education, or housing types.

Each DA will belong to one stratum, ensuring balanced representation across varying conditions.

#### **2. Clustering**

Clustering helps reduce logistical costs by grouping nearby units. Within each DA, use clustering to identify groups of addresses: 

  -  **Cluster size**: Define clusters of 5-10 addresses, ensuring clusters are small enough to capture local variability but large enough to reduce travel costs. 
  -  **Cluster selection**: Randomly select clusters within each DA.


#### **3. Random Sampling within Clusters**

From the selected clusters: 

  -  Conduct **simple random sampling** (SRS) to choose individual addresses. 
  -  The number of addresses sampled in each cluster should be proportional to the DA's population or specific needs. 
    -  At least 10% of address in each DA are sampled. 
    -  At least 30 addresses are sampled. If the number of addresses in the DA is less than 30, all addresses are sampled.

#### **4. Sample Size Determination**

Calculate the required sample size using: $\[ n = \frac{Z^2 \cdot p \cdot (1-p)}{E^2} \]$ Where: 

  -  $( Z )$ = Z-score (e.g., 1.96 for 95% confidence level). 
  -  $( p )$ = Estimated proportion of the population exhibiting the characteristic of interest (use pilot data if available). 
  -  $( E )$ = Margin of error (e.g., 5%).

Adjust the sample size to ensure that at least one cluster is selected per DA.

#### **5. Allocation of Sample**

Use **proportional allocation**: 

  -  Sample size in each $DA ( n_i ) = ( N_i/N \times n )$, where $( N_i )$ = population of $DA ( i )$, $( N )$ = total population, and $( n )$ = total sample size.

For sparsely populated DAs, consider **minimum allocation** (e.g., a fixed number of households per DA) to ensure representation.

#### *6. Conclusion*

Since theoretically, our sampling does not have any cost, we can skip stratification and clustering and make sure each our strata or cluster get sampled.

  -  Conduct **simple random sampling** (SRS) to choose individual addresses. 
  -  The number of addresses sampled in each DA should be proportional to the DA's population or specific needs. 
    -  At least 10% of address in each DA are sampled. 
    -  At least 30 addresses are sampled. If the number of addresses in the DA is less than 30, all addresses are sampled.

------------------------------------------------------------------------

### **Implementation Steps**

1.  **Data Preparation**
    -   Acquire the latest census data, including DA boundaries, population sizes, and socioeconomic indicators.
    -   Geocode all addresses to ensure accurate DA allocation.
2.  **Define Strata and Clusters**
    -   Stratify DAs based on predefined criteria.
    -   Divide each DA into clusters using geographic proximity.
3.  **Sample Selection**
    -   Randomly select DAs within each stratum.
    -   Randomly select clusters within each DA.
    -   Randomly sample addresses within clusters.
4.  **Survey Administration**
    -   Assign trained enumerators to visit selected addresses.
    -   Use standardized tools for data collection (e.g., mobile apps for geotagging responses).
5.  **Data Weighting and Analysis**
    -   Apply sampling weights to adjust for unequal probabilities of selection.
    -   Calculate DA-level averages and aggregate results to higher geographic levels.

------------------------------------------------------------------------

### **Addressing Distortion in DA-Level Averages**

To reduce distortion: - **Oversample** small DAs with high variability or unique characteristics. - **Post-stratify** data during analysis to ensure results align with known population distributions.

------------------------------------------------------------------------

### **Validation and Iteration**

Before full implementation: 1. Conduct a pilot study in a small region to validate the design. 2. Assess biases and variability in results. 3. Refine the sampling plan based on pilot findings.

------------------------------------------------------------------------

Would you like assistance with specific steps, such as determining sample size, creating strata, or implementing the survey?

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
